Distrivia: A Distributed Trivia Game

### 2011-03-25 papers/phase-zero/paper.tex
Lowercased 'of' in RIT label in latex file
remove synchronizer, add Riak

%\title{ Distributed Systems: Project Description }
\title{ Distrivia: A Distributed Trivia Game }
\numberofauthors{3}
\author{
\alignauthor
Brian Gianforcaro \\
       \affaddr{Rochester Institue Of Technology}\\
       \email{bjg1955@rit.edu}
\alignauthor
Steven Glazer \\
       \affaddr{Rochester Institue Of Technology}\\
       \email{sfg6126@rit.edu}
\alignauthor
Samuel Milton \\
       \affaddr{Rochester Institue Of Technology}\\
       \email{srm2997@rit.edu}
}
\maketitle

@@

\subsection{Backend}
The server has four key layers involved.
First, there will be a load balancer that accepts all messages from the players.
It does not need to read the contents of the message, it simply distributes the message on to the most reliable server with the lowest load.
This ensures that if any of the servers were to go down, that the system would still run.
It also maintains highest speeds for server response.
The message is passed to a web server from the load balancer, which will read the contents of the message and respond appropriately.
These messages will be in the form of http messages.
The web server communicates directly with the database to perform whatever actions need to be done.
The third layer is represented by these synchronous databases that hold all the actual data for the software.
This would include round information, player information, and all the questions for the application.
The fourth and final layer would be some sort of master process that does the
actual synchronization between the databases so that they all contain redudant data for reliable communication.

\begin{center}
  \includegraphics[scale=0.3]{design-pictures/database.png}
\end{center}

>>>>

%\title{ Distributed Systems: Project Description }
\title{ Distrivia: A Distributed Trivia Game }
\numberofauthors{3}
\author{
\alignauthor
Brian Gianforcaro \\
       \affaddr{Rochester Institue of Technology}\\
       \email{bjg1955@rit.edu}
\alignauthor
Steven Glazer \\
       \affaddr{Rochester Institue of Technology}\\
       \email{sfg6126@rit.edu}
\alignauthor
Samuel Milton \\
       \affaddr{Rochester Institue of Technology}\\
       \email{srm2997@rit.edu}
}
\maketitle

@@

\subsection{Backend}
The server has four key layers involved.
First, there will be a load balancer that accepts all messages from the players.
It does not need to read the contents of the message, it simply distributes the message on to the most reliable server with the lowest load.
This ensures that if any of the servers were to go down, that the system would still run.
It also maintains highest speeds for server response.
The message is passed to a web server from the load balancer, which will read the contents of the message and respond appropriately.
These messages will be in the form of http messages.
The web server communicates directly with the database to perform whatever actions need to be done.
The third layer is represented by these synchronous databases that hold all the actual data for the software.
This would include round information, player information, and all the questions for the application.
Currently we are looking at using Riak \cite{riak} for our database engine.
Riak has the unique ability to perform automatic masterless replication and
syncrhonization between all nodes of a database cluster. With this architecture 
all backend nodes except for one could fail and our system would remain
operational.
\begin{center}
  \includegraphics[scale=0.3]{design-pictures/database.png}
\end{center}
